Insert the article title here

### 2018-04-19 writeup/manuscript.tex
more results

Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}.
\end{fmtext}

@@

@@

@@

\subsection{Split-half Array Search}
Our results are broadly in line with \cite{nowakowsak2017}. The correlation between accuracy and reaction times between the two sessions is shown in Figure \ref{fig:splithalf_summary}(a, b). We can clearly see that there are large differences from one participant to the next in terms of both the proportion of hard targets found, and reaction times. Furthermore, test-retest reliability appears to be reasonable, with correlations of around $r = 0.78$ (the value of $r = 0.71$ or easy targets is slightly lower, likely due to the restricted range).

@@

\subsection{Adaptive Choice}

@@

@@

>>>>

\end{fmtext}

@@

Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}.

@@

A sample of 64 participants means we should be able to detect a correlations with $r > 0.342$ with $\alpha = 0.05$, $\beta = 0.80$ between the different visual search paradigms. Given the nature of our results, we see no need to apply a conservative correction for multiple comparisons.

@@

\subsection{Replication of each paradigm}

\subsubsection{Split-half Array Search}
Our results are broadly in line with \cite{nowakowsak2017}. The correlation between accuracy and reaction times between the two sessions is shown in Figure \ref{fig:splithalf_summary}(a, b). We can clearly see that there are large differences from one participant to the next in terms of both the proportion of hard targets found, and reaction times. Furthermore, test-retest reliability appears to be reasonable, with correlations of around $r = 0.78$ (the value of $r = 0.71$ or easy targets is slightly lower, likely due to the restricted range).

@@

\subsubsection{Adaptive Choice}

@@

\subsection{Correlations Between Paradigms}

The results above demonstrate that we have successfully replicated the previous findings around individual differences in visual search strategy. We now investigate whether there are correlations between paradigms: are individuals who are good at one visual search task good at another? We start by looking at simple reaction times (Figure \ref{fig:between_para_rt}). In all comparisons the correlations are weak, typically $0.27 < r <0.30$ but positive. None of these correlations are statistically significant ($p>0.05$). Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from paradigm to paradigm, the upper bound of $r=0.30$ this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.

\begin{figure}
\centering
\subfigure[][]{\includegraphics[width=5cm]{../Scripts/scratch/ls_v_ac_mean_log2rt.pdf}}
\subfigure[][]{\includegraphics[width=5cm]{../Scripts/scratch/ls_v_fg_conj_rt.pdf}}
\subfigure[][]{\includegraphics[width=5cm]{../Scripts/scratch/ac_v_fg_feature_rt.pdf}}
\subfigure[][]{\includegraphics[width=5cm]{../Scripts/scratch/ac_v_fg_conj_rt.pdf}}
\subfigure[][]{\includegraphics[width=5cm]{../Scripts/scratch/ls_v_ac_mean_log2rt.pdf}}
\caption{Correlation a) split-half and feature foraging; b) split-half and conjunction foraging, c) adaptive choice and feature  foraging; d) adaptive choice and conjunction foraging; e) split-half and adaptive choice. In all cases, these correlations are low, with $p>0.05$}
\label{fig:between_para_rt}
\end{figure}

Given the low correlations between reaction times, it seems unlikely that we will find that individuals who search efficiently and optimally in one paradigm will search well in another (the original motivation for our study). The analysis supports this hypothesis. For example, the correlation between the proportion of fixations to the heterogeneous side of the display in the split-half paradigm, and proportion of optimal targets found in the adaptive choice task is $r=-0.03$. Further results are presented in supplementary materials.

@@

The results presented above are somewhat surprising.
